---
title: "Week 4 Presentation"
author: "FairFax Team"
date: "6/15/2017"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(rgdal)
library(maptools)
library(ggplot2)
library(dplyr)
library(lubridate)
library(tidyr)
library(reshape2)
library(scales)
#library(OpenStreetMap)
library(osmar)
library(ggmap)
library(raster)
#library(rasterVis)
library(data.table)
library(RColorBrewer)
library(sp)
```

###Getting the Fairfax map

We need to convert it to Raster Brick Layer
https://rpubs.com/alobo/getmapCRS
```{r}
mgmap <- get_map(location=c(-77.7173, 38.5976, -76.8686, 39.0682), source = "google", color = "bw")
vgmap <- as.vector(mgmap)
vgmaprgb <- col2rgb(vgmap)
gmapr <- matrix(vgmaprgb[1, ], ncol = ncol(mgmap), nrow = nrow(mgmap))
gmapg <- matrix(vgmaprgb[2, ], ncol = ncol(mgmap), nrow = nrow(mgmap))
gmapb <- matrix(vgmaprgb[3, ], ncol = ncol(mgmap), nrow = nrow(mgmap))
rgmaprgb <- brick(raster(gmapr), raster(gmapg), raster(gmapb))
rm(gmapr, gmapg, gmapb)
projection(rgmaprgb) <- CRS("+init=epsg:4326")
proj4string(rgmaprgb) #Checking the Projection String
extent(rgmaprgb) <- unlist(attr(mgmap, which = "bb"))[c(2, 4, 1, 3)]
rgmaprgb
```

Getting GIS data for County, School and Zip
```{r warning=FALSE}

setwd("~/sdal/projects/limbo/fairfax_alerts/")
#County Shape File
county <- readShapePoly("GISData/Fairfax_County_Border/Fairfax_County_Border.shp",
                        proj4string=CRS('+proj=longlat +ellps=WGS84'))
#Zip Shape File
zip <- readShapePoly("GISData/ZIP_Codes/ZIP_Codes.shp",
                     proj4string=CRS('+proj=longlat +ellps=WGS84'))

#High School Shape File
highSchool <- readShapePoly("GISData/High_School_Pyramids/High_School_Attendance_Areas.shp",
                            proj4string=CRS('+proj=longlat +ellps=WGS84'))

#Convert Everything to the coordinate system for the raster map
county <- spTransform(county,rgmaprgb@crs)
zip <- spTransform(zip,rgmaprgb@crs)
highSchool <- spTransform(highSchool, rgmaprgb@crs)
```

### Plotting School and Zip code boundaries

```{r}
par(mfrow=c(1,1))
plot(highSchool, col = "red", main = "High School Boundary (red) \n vs Zipcode (green)")
lines(zip, col = "green")
```

###Mental Health Providers

Facilty appears to have the same name but different services and at times
different locations but, at other times, same location. Need to look through
and decide how we will count these mental health providers.
```{r}
mhp_clean <- rio::import("~/git/comm_fairfax/data/comm_fairfax/original/mhp_clean.csv")
#Data Duplication: How to clean this up. 
mhp_clean[7:10,]
```
We will look into other sources of mental health providers as well.

Converting MentalHealth To Spatial Data
```{r}
long_lat_mhp <- SpatialPoints(cbind(Long=as.numeric(mhp_clean$longitude), Lat=as.numeric(mhp_clean$latitude)))
long_lat_mhp_frame <- SpatialPointsDataFrame(cbind(lon = as.numeric(mhp_clean$longitude), lat = as.numeric(mhp_clean$latitude)),data = mhp_clean)
proj4string(long_lat_mhp_frame) <- proj4string(highSchool)
crs.geo <- CRS("+init=epsg:4326")
proj4string(long_lat_mhp) <- crs.geo

```

Overlay & Count
```{r}
#OVERLAY & COUNT
nrow(highSchool@data)
#Gives Associated Polygon for each Spatial Point
sch_with_mhp <- as.data.table(over(long_lat_mhp,highSchool))
mhp_per_sch <- sch_with_mhp[,.N,OBJECTID]
mhp_per_sch <- mhp_per_sch %>% left_join(highSchool@data, by = c("OBJECTID", "OBJECTID"))
highSchool_count <- highSchool@data %>% left_join(mhp_per_sch, by = c("OBJECTID","OBJECTID"))
```

### Plotting Mental Health Providers into High School Pyramid Regions

```{r}
plot(highSchool, asp = 1, main = "Mental Health Providers \n within High School Boundary")
points(mhp_clean$longitude, mhp_clean$latitude, pty =16, cex = 0.25, col = "red")
```

### Mental Health Provider by High School Pyramid

```{r warning ='hide', message = 'hide'}
plt <- ggplot(data = mhp_per_sch, aes (x=SCHOOL_NAM, y = N, fill = N)) +
    geom_bar(stat = "identity") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle=90, hjust =1, vjust=0.5, size = 7.5), panel.grid.major = NULL) + ggtitle("Count of Mental Health Providers \n by High School Pyramid") +
    labs(y= "Number of Mental \n Health Providers", x = "High School Name") +
    scale_y_discrete(limits=1:10, labels = 1:10) +
    scale_fill_gradient2(low = '#d8b365', mid = '#808080', high = '#5ab4ac', midpoint = 5)
suppressWarnings(print(plt))
```

### HeatMap 
### Interesting fact for the week:
### Let's DRAW a ACS INCOME MAP BY SCHOOL BOUNDARY TO CATCH the Rich folks AT MCCLEAN!
```{r}
#Based on Bianica's Code
names(highSchool@data)
highSchool@data$id <- rownames(highSchool@data)
highSchool@data$id

#Convert Polygon information into data frame is what fortify does
highSchool.points <- fortify(highSchool)
names(highSchool.points)

highSchool.df <- left_join(highSchool.points, highSchool@data, by = "id")
highSchool.df <- left_join(highSchool.df, mhp_per_sch, by = "OBJECTID")

#CAN WE CONFIRM THE NUMBERS BY LOOKING AT THE MAP (FROM BEN: ONLINE), the table we built MHP table above and the DENSITY VOLUMES HERE?

#JEFFERSON HIGH SCHOOL IS IN THE LOW TRIANGLE
mhp_per_sch
plt <-ggplot(highSchool) + 
    geom_polygon(data = highSchool.df, aes(x = long, y = lat, group = OBJECTID, fill = N), color = "red") + labs(title = "Mental Health Providers Heat Map \n by High School Pyramid") 
suppressWarnings(print(plt))
```
###Which High School Pyramids do not have Mental Health Providers

8 High School Pyramids. 7 on the map? Where goes the missing one? :(
```{r}
nrow(highSchool@data[!(highSchool@data$SCHOOL_NAM %in% mhp_per_sch$SCHOOL_NAM),])
```

### High School Pyramids with no Mental Health Providers
```{r}
schools <- highSchool@data[!(highSchool@data$SCHOOL_NAM %in% mhp_per_sch$SCHOOL_NAM),]
nrow(schools)
schools$SCHOOL_NAM
```




